### 2016-09-22 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
removed box formatting around definitions of corpora following Plos One instructions

\vspace{0.25cm}
\begin{center}
\fbox{
\begin{minipage}{0.8\linewidth}
\textbf{Creativity corpus}: \\ a collection of thirty academic papers which explicitly discuss the nature of creativity.
\end{minipage}
}
\end{center}
\vspace{0.25cm}

@@

\vspace{0.25cm}
\begin{center}
\fbox{
\begin{minipage}{0.8\linewidth}
\textbf{Non-creativity corpus}: \\ 60 academic papers on topics unrelated to creativity, from the  same range of academic disciplines and publication years as  the creativity corpus papers.
\end{minipage}
}
\end{center}
\vspace{0.25cm}

>>>>

\begin{itemize}
\item[] {\em \textbf{Creativity corpus}: a collection of thirty academic papers which explicitly discuss the nature of creativity.\\}
\end{itemize}
%\vspace{0.25cm}
%\begin{center}
%\fbox{
%\begin{minipage}{0.8\linewidth}
%
%\end{minipage}
%}
%\end{center}
%\vspace{0.25cm}

@@

%\vspace{0.25cm}
%\begin{center}
%\fbox{
%\begin{minipage}{0.8\linewidth}
\begin{itemize}
\item[] {\em \textbf{Non-creativity corpus}:  a collection of sixty academic papers on topics unrelated to creativity, from the  same range of academic disciplines and publication years as  the creativity corpus papers.}
\end{itemize}
%\end{minipage}
%}
%\end{center}
%\vspace{0.25cm}
